% Conclusion
\section{Conclusion}


The project goal were to create clothes registering interface and robot arm control by using sorting algorithm. A flexible database and sorting algorithm was created, that collaborates with the other subtasks. The sorting algorithm achieves the set goal, parameters and future improvements have been documented. The goals were achieved by closely collaborating with the groups of subtasks 4 and 6. 
\\ \\
Bellow implemented parts:
\\
\begin{itemize}
	\item We got introduced to and understood the basic principles of MySQL Data base system. ER and UML diagrams were also designed. By using the MySQL language a data base was created and tested.

	\item By using C\# and MySQL .NET connector tool a MySQL library was created which communicates with a MySQL data base. All functionalities of the MySQL library were achieved and tested.

	\item By using C\# a Socket transfer server was created and a communication protocol was also defined. Socket transfer server is used for controlling robot arm.

	\item The main task of the project was to create a sorting algorithm. By using a Sorting algorithm all clothes are sorted and information about BinID is stored into the
database. The implemented algorithm sorts the clothes by color and washing temperature information. A more advanced sorting algorithm is explained which could be optimal and improve flexibility..

	\item By using C\# and .dll libraries a control logic was created for RFID readers. The control logic has a reliable clothes reading function, that prepares a list for the sorting algorithm to process.
\end{itemize}

