% Conclusion
\section{Conclusion}
The project goal were to create clothes registering interface and robot arm
control by using sorting algorithm. To achieve mentioned goals were closely
colaboreted between subtasks 4 and 6. Bellow implemented parts:

We introduced and understood basic
principles of MySQL Data base system. Also was designed ER and UML diagrams. By using MySQL language was created data base and tested.

By using C# and MySQL .NET connector tool was created MySQL library which comunicates with MySQL data base. All functionalies of MySQL library were achieved and tested.

By using C# was created Socket transfer server and also defned comunication protocol. Socket transfer server is used for controling robot arm.

The main task of the project was to create a sorting algorithm. By using Sorting algorithm all clothes are sorted and information about BinID is stored into
database. Implemented algorithm sorts by color and washing temperature's information of clothes. Later on, is offered and explained more advanced sorting algorithm which could be optimal and improve flexibility.

RFID reader control. By using C# and .dll libraries was created control logic. Control logic takes care of reliable clothes' reading.



A flexible database and sorting algorithm was created, that collaborates with the other subtasks. The sorting algorithm achieves the set goal, parameters and future improvements have been documented. The goals were achieved by closely collaborating with the groups of subtasks 4 and 6. 
\\
Bellow implemented parts:
\begin{enumerate}
	\item We introduced to MySQL Data base system and understanded basic principles. Also were designed ER and UML diagrams. By using MySQL language were created data base and tested.
	\item By using C\# and MySQL .NET connector were created mySQL library which comunicates with MySQL data base. All functionalies of MySQL library were achieved and tested. Regarding this clothe registering interface were created.
	\item By using C\# were created Socet transfer server and also defined comunication protocol. Throw Socket transfer server were controled robot arm.
	\item Main task were to create a sorting algorithm. By using Sorting algoriithm all clothes sorted and information about BinID stored into database. Implemented algorithm sorting by color and washing temperature. later offered and explained more advance sorting algorithm which can be more optimal and flexible.
	\item RFID reader control. By using C\# and .dll libraries were created control logic. Control logic take care of relable clothe read.
\end{enumerate}